Tactic Script Optimisation for Aesop

### 2024-09-10 paper.tex
Add indentation of continued lines in algorithms

\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage[british]{babel}
\usepackage{csquotes}
\usepackage{subcaption}
\usepackage{microtype}
\usepackage{newunicodechar}
\usepackage[plain]{algorithm}
\usepackage{algpseudocodex}
\usepackage{mathtools}

@@

\newcommand{\tac}[1]{\ensuremath{\mathrm{\mathcolor{blue}{#1}}}}
\newcommand{\Lam}[2]{λ\,#1,\; #2}
\newcommand{\mvar}[1]{{?#1}}
\newcommand{\pre}{\mathrm{pre}}
\newcommand{\post}{\mathrm{post}}
\newcommand{\tacbullet}{\vcenter{\hbox{\scalebox{.7}{$\bullet\;\;$}}}}
\newcommand{\step}[5]{\ensuremath{(#1,\allowbreak #2,\allowbreak #3,\allowbreak #4,\allowbreak #5)}}
\newcommand{\aeq}{\hat{≡}}
\newcommand{\dom}{\ensuremath{\mathrm{dom}}}

@@

@@

    \Function{next-step}{$\mathit{tacticState}, \mathit{steps}$}
      \State \Let $g$ be the first goal in $\mathit{tacticState}$
      \If{$g$ does not contain metavariables}
        \State \Return the step for $g$
      \Else
        \State \Return the first step whose pre-goal is contained in $\mathit{tacticState}$
      \EndIf
    \EndFunction

@@

    \Function{apply-step}{$\mathit{tacticState}, (Φ, g, t, Ψ, G)$}
      \State \Let $\mathit{tacticState}$ be $[g₁, \dots, gₙ, g, h₁, \dots, hₘ]$
      \State \Let $G$ be $[k₁, \dots, kₗ]$
      \State $r \gets [g₁, ..., gₙ, k₁, \dots, kₗ, h₁, \dots, hₘ]$
      \State Remove from $r$ each goal $x$ such that $x$ is assigned in $Ψ$ but not in $Φ$
      \State \Return $r$
    \EndFunction
  \end{algorithmic}
  \caption{Static reordering}\label{alg:static-reordering}
\end{algorithm}

@@

    \Function{apply-step}{$\mathit{steps}, Φ, G, g, s$}
      \State \Let step $s$ be $(Φ^{\pre}, g, t, Φ^{\post}, G^{\post})$
      \State Run $t$ in tactic state $(Φ, [g])$, producing tactic state $(Ψ, G')$
      \If{$(Φ^{\post}, G^{\post}) \aeq (Ψ, G')$}
        \State \Let $σ$ be the partial map from metavariables in $Φ^{\post}$ to matching metavariables in $Ψ$
        \State For each step in $\mathit{steps}$, replace its pre-goal $g^{\pre}$ with $σ(g^{\pre})$ if $g^{\pre} ∈ \dom(σ)$
        \State $s' \gets (Φ, g, t, Ψ, G')$
        \State \Let $G$ be $[g₁, \dots gₙ, g, k₁, \dots, kₘ]$
        \State \Let $G'$ be $[h₁, \dots, hₗ]$
        \State $H \gets [g₁, \dots, gₙ, h₁, \dots, hₗ, k₁, \dots, kₘ]$
        \State Remove from $H$ each goal that is assigned in $Ψ$
        \State $(\mathit{script}, Ω) \gets \Call{reorder-dynamic}{\mathit{steps}, Ψ, H}$
        \State \Return $(s' ∷ \mathit{script}, Ω)$
      \Else
        \State \Failure
      \EndIf
    \EndFunction
  \end{algorithmic}
  \caption{Dynamic reordering}\label{alg:dynamic-reordering}
\end{algorithm}

>>>>

\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage[british]{babel}
\usepackage{csquotes}
\usepackage{subcaption}
\usepackage{microtype}
\usepackage{newunicodechar}
\usepackage[plain]{algorithm}
\usepackage{algpseudocodex}
\usepackage{mathtools}
\usepackage{calc}

@@

\newcommand{\tac}[1]{\ensuremath{\mathrm{\mathcolor{blue}{#1}}}}
\newcommand{\Lam}[2]{λ\,#1,\; #2}
\newcommand{\mvar}[1]{{?#1}}
\newcommand{\pre}{\mathrm{pre}}
\newcommand{\post}{\mathrm{post}}
\newcommand{\tacbullet}{\vcenter{\hbox{\scalebox{.7}{$\bullet\;\;$}}}}
\newcommand{\step}[5]{\ensuremath{(#1,\allowbreak #2,\allowbreak #3,\allowbreak #4,\allowbreak #5)}}
\newcommand{\aeq}{\mathrel{\hat{≡}}}
\newcommand{\dom}{\ensuremath{\mathrm{dom}}}

@@

% Indentation for continuation lines in algorithm environments
\newlength{\cindentlen}
\setlength{\cindentlen}{1em}
\newcommand{\cindent}{\hspace{\cindentlen}}

@@

    \Function{next-step}{$\mathit{tacticState}, \mathit{steps}$}
      \State \Let $g$ be the first goal in $\mathit{tacticState}$
      \If{$g$ does not contain metavariables}
        \State \Return the step for $g$
      \Else
        \State \Return the first step whose pre-goal is contained
        \State \hspace{\widthof{\Return}} \cindent in $\mathit{tacticState}$
      \EndIf
    \EndFunction

@@

    \Function{apply-step}{$\mathit{tacticState}, (Φ, g, t, Ψ, G)$}
      \State \Let $\mathit{tacticState}$ be $[g₁, \dots, gₙ, g, h₁, \dots, hₘ]$
      \State \Let $G$ be $[k₁, \dots, kₗ]$
      \State $r \gets [g₁, ..., gₙ, k₁, \dots, kₗ, h₁, \dots, hₘ]$
      \State Remove from $r$ each goal $x$ such that $x$ is assigned in
      \State \cindent $Ψ$ but not in $Φ$
      \State \Return $r$
    \EndFunction
  \end{algorithmic}
  \caption{Static reordering}\label{alg:static-reordering}
\end{algorithm}

@@

    \Function{apply-step}{$\mathit{steps}, Φ, G, g, s$}
      \State \Let step $s$ be $(Φ^{\pre}, g, t, Φ^{\post}, G^{\post})$
      \State Run $t$ in tactic state $(Φ, [g])$, producing tactic state
      \State \cindent $(Ψ, G')$
      \If{$(Φ^{\post}, G^{\post}) \aeq (Ψ, G')$}
        \State \Let $σ$ be the partial map from metavariables in $Φ^{\post}$
        \State \hspace{\widthof{\Let}} \cindent to matching metavariables in $Ψ$
        \State For each step in $\mathit{steps}$, replace its pre-goal $g^{\pre}$
        \State \cindent with $σ(g^{\pre})$ if $g^{\pre} ∈ \dom(σ)$
        \State $s' \gets (Φ, g, t, Ψ, G')$
        \State \Let $G$ be $[g₁, \dots gₙ, g, k₁, \dots, kₘ]$
        \State \Let $G'$ be $[h₁, \dots, hₗ]$
        \State $H \gets [g₁, \dots, gₙ, h₁, \dots, hₗ, k₁, \dots, kₘ]$
        \State Remove from $H$ each goal that is assigned in $Ψ$
        \State $(\mathit{script}, Ω) \gets \Call{reorder-dynamic}{\mathit{steps}, Ψ, H}$
        \State \Return $(s' ∷ \mathit{script}, Ω)$
      \Else
        \State \Failure
      \EndIf
    \EndFunction
  \end{algorithmic}
  \caption{Dynamic reordering}\label{alg:dynamic-reordering}
\end{algorithm}
